Meta-analysis

### 2019-09-19 01_Meta-analysis_experiments.Rmd
Edits reviewed and accepted

```{r MEsummary_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(leaflet)
#source("./getPPD2.R")

@@

```{r}
knitr::kable(cbind(
   Acronym = c("SF", "Ti", "AX", "Ca"),
   Expected_Fungicide = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
   Active_Ingredient = c(
      "Sulphur",
      "Propiconazole",
      "Azoxystrobin and Cyproconazole",
      "Carbendazim"
   )
))
```

@@

PM.dat <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv")

@@

kable(
   PM.dat %>%
      group_by(
         Trial_ref,
         Year,
         Location,
         trial_design,
         Replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(Treatments = length(E_treatment)),
   caption = "Description of Experiments"
) %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

PM.dat$Trial_ref <- factor(PM.dat$Trial_ref)
PM.dat$Location <- factor(PM.dat$Location)
PM.dat$Year <- factor(PM.dat$Year)
PM.dat$host_genotype <- factor(PM.dat$host_genotype)
PM.dat$Fungicide <- factor(PM.dat$Fungicide)
PM.dat$Trade_name <- factor(PM.dat$Trade_name)
```

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage",
      "Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College"
   ),
   lat = c(-28.215 , -26.58, -27.56, -23.54),
   lon = c(152.1003, 151.83, 152.32, 148.19)
)

>>>>

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
library(dplyr)
library(readr)
library(kableExtra)
library(leaflet)
source("R/import_data.R")
```

@@

```{r}
knitr::kable(cbind(
   Acronym = c("SF", "Ti", "AX", "Ca"),
   `Expected Fungicide` = c("Sulphur", "Tilt", "Amistar Xtra", "Carbendazim"),
   `Active Ingredient` = c(
      "Sulphur",
      "Propiconazole",
      "Azoxystrobin and Cyproconazole",
      "Carbendazim"
   )
))
```

@@

PM.dat <- import_data()

@@

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(e_treatment)),
   caption = "Description of Experiments"
) %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

@@

```{r Experiment_locations}
experiment_sites <- data.frame(
   location = c(
      "Hermitage Research Station",
      "Kingaroy Research Station",
      "Gatton",
      "Emerald Agricultural College"
   ),
   lat = c(-28.215 , -26.58, -27.56, -23.54),
   lon = c(152.1003, 151.83, 152.32, 148.19)
)
